Optimizing a PoS Tag Set for Dependency Parsing

### 2016-05-04 submission.tex
Minor changes

\section{Data}
\label{sec:data}
\subsection{The Norwegian Dependency Treebank}
We used the newly developed Norwegian Dependency Treebank (NDT)
\cite{Sol:Skj:Ovr:14},  the first publicly available treebank for Norwegian. It
was developed at the National Library of Norway in collaboration with the
University of Oslo, and contains manual syntactic and morphological annotation.
The treebank contains data from both varieties of Norwegian; 311 000 tokens of
Bokmål and 303 000 tokens of Nynorsk. The annotated texts are mostly newspaper
text, but also include government reports, parliament transcripts and excerpts
from blogs. The annotation process of the treebank was supported by the
Oslo-Bergen Tagger \cite{Hag:Joh:Nok:00} and then manually corrected by
annotators.

>>>>

\section{The Norwegian Dependency Treebank}
\label{sec:data}
We used the newly developed Norwegian Dependency Treebank (NDT)
\cite{Sol:Skj:Ovr:14}, the first publicly available treebank for
Norwegian. It was developed at the National Library of Norway in
collaboration with the University of Oslo, and contains manual
syntactic and morphological annotation.  The treebank contains data
from both varieties of Norwegian; 311 000 tokens of Bokmål and 303 000
tokens of Nynorsk. We will in the following only be using the Bokmål
portion of the treebank. The annotated texts are mostly newspaper
text, but also include government reports, parliament transcripts and
excerpts from blogs. The annotation process of the treebank was
supported by the rule-based Oslo-Bergen Tagger \cite{Hag:Joh:Nok:00}
and then manually corrected by annotators, adding syntactic dependency analysis
to the morphosyntactic annotation.
